What Happened to The Birth Rate?

### 2022-02-28 outputs/paper/paper.Rmd

Figure \@ref(fig:fig-lgbt-trend-by-year) shows the trend of LGBT population percentage in total population.
There is an obvious increasing trend (i.e. higher percentage of the US population are becoming LGBT). 
Figure \@ref(fig:fig-lgbt-by-generation) shows the percentage of LGBT population trend in different generations.
We can also see an increasing trend of LGBT population percentage (younger generations are more and more likely to become LGBT).
This provide more evidence that cohort effects may contribute to the delines of birth rate in the US in recent years.

>>>>

## LGBT and Cohort Effect

Figure \@ref(fig:fig-lgbt-trend-by-year) shows the trend of LGBT population percentage in total population.
There is an obvious increasing trend (i.e. higher percentage of the US population are becoming LGBT) [@us_lgbt_trend].
Figure \@ref(fig:fig-lgbt-by-generation) shows the percentage of LGBT population trend in different generations [@us_lgbt_trend].
We can also see an increasing trend of LGBT population percentage (younger generations are more and more likely to become LGBT).
This provides more evidence that cohort effects and the growth of LGBT population may have contributed a lot to the declines of birth rate in the US in recent years.
